---
title: "Using GausSKAT"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using GausSKAT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

GausSKAT evaluates a phenotype-independent, data-adaptive grid of weighted
Gaussian kernels and combines their SKAT p-values with ACAT. The lower endpoint
is the median strictly positive weighted genetic distance. The practical upper
endpoint is a first-order approximation based on stabilization of the
Frobenius-scaled, covariate-adjusted kernel.

```{r example, eval=FALSE}
library(SKAT)
library(GausSKAT)

data("SKAT.example", package = "SKAT")
null_model <- SKAT_Null_Model(
  y.c ~ X,
  data = SKAT.example,
  out_type = "C"
)

fit <- GausSKAT(
  SKAT.example$Z,
  null_model,
  parallel = TRUE,
  n_cores = 5L
)
fit$p.value
fit$component.p.values
fit$ell.grid
fit$delta.at.ell.max
```

The package passes the constructed kernel matrices to the official `SKAT`
package. It does not alter SKAT's null-model fitting or p-value calculations.
Component tests can be evaluated sequentially or in parallel. Parallel runs
use forked workers on macOS/Linux and PSOCK workers on Windows.
